---
title: "Read data from MySQL DB"
author: "Vebash Naidoo"
date: "29/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(DBI)
```

## What ODBC Drivers do we have?

```{r}
sort(unique(odbc::odbcListDrivers()[[1]]))
```

## Let's connect via RStudio's `Connections` pane

1. We can make an `odbc` connection.
1. Go to [connection strings](https://www.connectionstrings.com/) to find the appropriate connection string to use.
1. Choose your DB, here we'll choose `MySQL`.
1. Copy the __Specifying TCP port__ string.
1. Click on the "Connections" tab - mine is with the `Environment`, `Files`, `Git` tabs in RStudio.
1. Choose `New Connection` -> `MySQL...`
1. Paste the copied TCP string in the `Parameters` box. Notice that when you press test the string you added is appended to the `.connection_string` parameter.
1. Copy the connection string created in this process onto your clipboard.

```{r}
# The connection string as per the `New Connection` 
# process
con <- dbConnect(odbc::odbc(), 
                 .connection_string = "Driver={MySQL ODBC 8.0 Unicode Driver};Server=localhost;Port=3306;Database=starwars;Uid=admin;Pwd=Luke1@my0urf@ther;", 
                 timeout = 10)
```

```{r}
tbl(con, "characters") %>% 
  left_join(tbl(con, "appearances")) %>% 
  left_join(tbl(con, "films"),
            by = c("film_id" = "id")) %>% 
  glimpse()
```


```{r}
dbDisconnect(con)
```

